---
title: "Convert Images to Tensors"
date: "17.11.2020"
output: github_document
---

*NOTE:* Use these functions `ANTsRNet::resampleTensor`, `reticulate::array_reshape`

```{r, include = FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/10_images_to_tensors-",
  out.width = "100%"
)

`%>%` <- purrr::`%>%`

library(tidyverse, warn.conflicts = FALSE)
library(ANTsRCore)

library(devtools)
library(fs)

library(rraysplot)
```


## Image data for U-Net

Source [2.2.11 Data representations for neural networks](https://livebook.manning.com/book/deep-learning-with-r/chapter-2/48)
in [Deep Learning with R](https://www.manning.com/books/deep-learning-with-r) by
François Chollet with J. J. Allaire.

Images typically have three dimensions:
```
height × width × color channels
```
Although grayscale images have only a single color channel 
and could thus be stored in 2D tensors, by convention 
image tensors are always 3D, with a one-dimensional color channel
for grayscale images. 

A batch of 80 grayscale images of size 768×384 could thus
be stored in a tensor of shape 
```
(80, 768, 384, 1)
```
and a batch of 80 color images could be stored in a tensor of shape
```
(80, 768, 384, 3)
```
and a batch of 80 mask --
```
(80, 768, 384, 2)
```


## Important Note

We will crop all images to 768x384 and prepare additional data with resampled (smaller)
images: 384x192 and 192x96. Note that both dimensions 768x384 are divisble by 128
(768/2^7=6, 384/2^7=3).


## Read Images Info

```{r, rows.print=10}
info <- images_info("../80_images", extension = "dcm")
info
```

```{r, rows.print=10}
info_mri <- info %>% filter(kind == "MRI")
info_mri
```

```{r, rows.print=10}
info_at <- info %>% filter(kind == "AT")
info_at
```

```{r}
crop_image_wxhx1 <- function(img, ll = c(34, 56), wh = c(768, 384)) {
  ll = c(ll, 1)                        # c(34, 56, 1)
  ur = ll + c(wh, 0) - c(1, 1, 0)      # c(768 - 1, 384 - 1, 0)
  ANTsRCore::cropIndices(img, ll, ur)
}

crop_image_wxh <- function(img, ll = c(34, 56), wh = c(768, 384)) {
  ur = ll + wh - c(1, 1)               # c(768 - 1, 384 - 1)
  ANTsRCore::cropIndices(img, ll, ur)
}
```


## MRI images

```{r}
mri_list <- imageFileNames2ImageList(info_mri[["file_path"]])
length(mri_list)
```

```{r}
crop_image_wxhx1 <- function(img, ll = c(34, 56), wh = c(768, 384)) {
    ll = c(ll, 1)                   # c(34, 56, 1)
    ur = ll + c(wh, 0) - c(1, 1, 0) # c(768 - 1, 384 - 1, 0)
    ANTsRCore::cropIndices(img, ll, ur)
}

get_channel <- function(img, channel = 1) {
  ANTsRCore::splitChannels(img)[[channel]]
}
  
(img = crop_image_wxhx1(mri_list[[1]]))
(channel1 = get_channel(img, channel = 1))
(slice = ANTsRCore::extractSlice(channel1, slice = 1, direction = 3))
(smask = ANTsRCore::getMask(slice))
```

```{r}
plot_array2d(as.array(smask))
invisible(plot(slice, smask, doCropping = FALSE))
```

```{r}
images_to_tensor_mask <- function(iList, ll = c(34, 56), width_x_height = c(768, 384), channel = 1) {
  get_channel <- function(img, channel = 3) {
    ANTsRCore::splitChannels(img)[[channel]]
  }
  get_mask <- purrr::compose(ANTsRCore::getMask, get_channel)
  
  mList <- purrr::map(iList, get_mask, channel = 1)
  mList
}
```

```{r}
images_to_tensor <- function(iList, lower_left = c(34, 56), width_x_height = c(768, 384), channel = 1) {
  crop_image_wxhx1 <- function(img, ll = lower_left, wh = width_x_height) {
    ll = c(ll, 1)                               # c(34, 56, 1)
    ur = ll + c(width_x_height, 0) - c(1, 1, 0) # c(768 - 1, 384 - 1, 0)
    ANTsRCore::cropIndices(img, ll, ur)
  }

  n_images <- length(iList)
    
  domainImage = ANTsRCore::makeImage(imagesize = width_x_height, voxval = 0)
  dims = dim(domainImage)

  y_train <- array(
    data = NA,
    dim = c(components(iList[[1]]), dims, n_images)
  )

  array_crop <- purrr::compose(as.array, crop_image_wxhx1)
  aList <- map(iList, array_crop, ll = lower_left, wh = width_x_height)

  for (i in seq_along(aList)) {
    y_train[,,,i] <- aList[[i]]
  }

  K <- keras::backend()  

  y_train <- as.array(
    K$permute_dimensions(y_train, pattern = c(3L, 1L, 2L, 0L))
  )

  dimnames(y_train)[[1]] <- info$patient

  y_train[,,,channel]
}
```


```{r}
train <- images_to_tensor(mri_list)
str(train)
```

```{r}
mask <- images_to_tensor_mask(info_mri)
str(mask)
```


## Check if dimnames are parallel to image indexes

```{r figures2-side2, fig.show="hold", fig.asp=0.5, out.width="48%"}
plot_array2d(train[5,,], title = dimnames(train)[[1]][[5]])
plot_array2d(train[29,,], title = dimnames(train)[[1]][[29]])
```

```{r figures2-side3, fig.show="hold", fig.asp=0.5, out.width="48%"}
plot_array2d(train[46,,], title = dimnames(train)[[1]][[46]])
plot_array2d(train["700120",,], title = dimnames(train)[[1]][[46]])
```


## TODO

```{r}
p <- info$file_path[[1]]
img <- ANTsRCore::antsImageRead(p)
channels <- ANTsRCore::splitChannels(img)
slice <- ANTsRCore::extractSlice(channels[[1]], 1, 3)
cslice <- crop_image_wxh(slice)
aslice = as.array(cslice)

dim(cslice)
dim(aslice)
```

```{r, figures2-side1, fig.show="hold", fig.asp=0.5, out.width="48%"}
plot_array2d(aslice)
invisible(plot(cslice, doCropping=F))
```

