---
title: "Convert Images to Tensors"
date: "15.11.2020"
output: github_document
---

*NOTE:* ANTsRNet::resampleTensorLike, ANTsRNet::resampleTensor,
keras::array_reshape, reticulate::array_reshape

```{r, include = FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/10_images_to_tensors",
  out.width = "100%"
)

`%>%` <- purrr::`%>%`

library(tidyverse)
library(ANTsRCore)

library(devtools)
library(fs)

library(rraysplot)
# source("R/plot_array2d.R")
# source("R/images_info.R")
```


## Image data for U-Net [2.2.11](https://livebook.manning.com/book/deep-learning-with-r/chapter-2/48)

Images typically have three dimensions:
```
height × width × color channels
```
Although grayscale images have only a single color channel 
and could thus be stored in 2D tensors, by convention 
image tensors are always 3D, with a one-dimensional color channel
for grayscale images. 

A batch of 80 grayscale images of size 768×384 could thus
be stored in a tensor of shape 
```
(80, 768, 384, 1)
```
and a batch of 80 color images could be stored in a  tensor of shape
```
(80, 768, 384, 3)
```

*NOTE:* 768/2^7=6, 384/2^7=3.


## Read file names of images

```{r, rows.print=8}
info <- images_info("../80_images", extension = "dcm") %>% 
  dplyr::slice(1:16)
info
```

```{r}
crop_image_768x384x1 <- function(img) {
  ll = c(34, 56, 1)
  ur = ll + c(768 - 1, 384 - 1, 0)
  ANTsRCore::cropIndices(img, ll, ur)
}

crop_image_768x384 <- function(img) {
  ll = c(34, 56)
  ur = ll + c(768 - 1, 384 - 1)
  ANTsRCore::cropIndices(img, ll, ur)
}
```

## Base images

```{r}
base_paths <- info %>% filter(kind == "base")
iList <- imageFileNames2ImageList(base_paths[["file_name"]])
n_images <- length(iList)

Y_train <- array(
  data = NA, 
  dim = c(3, 768, 384, n_images)
)
```


```{r}
p <- info$file_name[[1]]
img <- ANTsRCore::antsImageRead(p)
channels <- ANTsRCore::splitChannels(img)
slice <- ANTsRCore::extractSlice(channels[[1]], 1, 3)
cslice <- crop_image_768x384(slice)
aslice = as.array(cslice)

plot_array2d(aslice)
invisible(plot(cslice, doCropping=F))
```

```{r}
K <- keras::backend()
array_crop <- purrr::compose(as.array, crop_image_768x384x1)
aList <- map(iList, array_crop)

for (i in seq_along(aList)) {
  Y_train[,,,i] <- aList[[i]]
}
Y_train <- as.array(
  K$permute_dimensions(Y_train, pattern = c(3L, 1L, 2L, 0L))
)

dimnames(Y_train)[[1]] <- base_paths$patient
```

```{r}
dim(Y_train)
dimnames(Y_train)[[1]]
dim(Y_train[3,,,1])
dim(Y_train["1040979",,,1])

```

```{r}
for(name in dimnames(Y_train)[[1]]) {
  cat(name, "\n")
}
```

```{r}
plot_array2d(Y_train[3,,,1])
plot_array2d(Y_train["1040979",,,1])
```
