---
title: "Convert Images to Tensors"
date: "19.11.2020"
output:
  html_document:
    keep_md: TRUE
    keep_html: TRUE
    df_print: paged
  pdf_document: default
---

```{r, include = FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/10_images_to_tensors-",
  out.width = "100%"
)

`%>%` <- purrr::`%>%`

library(tidyverse, warn.conflicts = FALSE)
library(ANTsRCore)

library(devtools)
library(lobstr)
library(fs)

library(rraysplot)
packageVersion("rraysplot")
```


## Image data for U-Net

Source [2.2.11 Data representations for neural networks](https://livebook.manning.com/book/deep-learning-with-r/chapter-2/48)
in [Deep Learning with R](https://www.manning.com/books/deep-learning-with-r)
by François Chollet with J. J. Allaire.

Images typically have three dimensions:
```
height × width × color channels
```
Although grayscale images have only a single color channel
and could thus be stored in 2D tensors, by convention
image tensors are always 3D, with a one-dimensional color channel
for grayscale images.

A batch of 80 grayscale images of size 768×384 could thus
be stored in a tensor of shape
```
(80, 768, 384, 1)
```
and a batch of 80 color images could be stored in a tensor of shape
```
(80, 768, 384, 3)
```
and a batch of 80 mask --
```
(80, 768, 384, 2)
```


## Important Note

We will crop all images to the 768x384 size and 
prepare tensors for U-Net NN in dimensions:
```
768x384, 384x192 and 192x96
```

Note that both dimensions 768x384 are divisble by 128
(768/2^7=6, 384/2^7=3).


## Helper functions

```{r}
crop_image_wxhx1 <- function(img, ll = c(34, 56), wh = c(768, 384)) {
  ll = c(ll, 1)
  ur = ll + c(wh, 0) - c(1, 1, 0)
  ANTsRCore::cropIndices(img, ll, ur)
}

get_channel <- function(img, channel = 1) {
  ANTsRCore::splitChannels(img)[[channel]]
}

imageList2sliceList <- function(
    iList,
    channel = 1,
    z_slice = 1,
    do_cropping = TRUE,
    lower_left = c(34, 56),
    width_x_height = c(768, 384)
) {
  if (do_cropping == TRUE) {
    iList <- purrr::map(
      iList,
      crop_image_wxhx1, ll = lower_left, wh = width_x_height
    )
  }
  iList <- purrr::map(iList, get_channel, ch = channel)
  iList <- purrr::map(iList,
    ANTsRCore::extractSlice, slice = z_slice, direction = 3
  )
}

imageList2MaskList <- function(iList, clean_up = 2) {
  purrr::map(iList, ANTsRCore::getMask, cleanup = clean_up)
}

imageList2arrayList <- function(iList) {
  purrr::map(iList, as.array)
}

arrayList2Tensor <- function(aList, dim_names = info_mri$patient) {
  tensor <- array(
    data = NA,
    dim = c(length(aList), dim(aList[[1]]))
  )

  for (i in seq_along(aList)) {
    tensor[i,,] <- aList[[i]]
  }
  dimnames(tensor)[[1]] <- dim_names

  tensor
}
```


## Read Images Info

```{r}
info <- images_info("../80_images", extension = "dcm")
```

```{r, rows.print=2}
info_mri <- info %>% filter(kind == "MRI")
info_mri
```

```{r, rows.print=2}
info_scat <- info %>% filter(kind == "SCAT")
info_scat
```

```{r, rows.print=2}
info_vsat <- info %>% filter(kind == "VSAT")
info_vsat
```


## Create Images and Mask Lists

```{r}
mri_list  <- imageFileNames2ImageList(info_mri[["file_path"]]) %>%
  imageList2sliceList(channel = 1)
mask_list <- imageList2MaskList(mri_list, clean_up = 2)

scat_list <- imageFileNames2ImageList(info_scat[["file_path"]]) %>%
  imageList2sliceList(channel = 1) %>%
  imageList2MaskList(clean_up = 0)

vsat_list <- imageFileNames2ImageList(info_vsat[["file_path"]]) %>%
  imageList2sliceList(channel = 3) %>%
  imageList2MaskList(clean_up = 0)
```

We are going to remove the background noise from image.

The background noise present (left) and removed (right).

```{r figures-bgnoise, fig.show="hold", fig.asp=1, out.width="25%"}
invisible(plot(mri_list[[1]], doCropping = FALSE))
bhistogram(as.array(mri_list[[1]]))

mri_list2 <- purrr::map2(mri_list, mask_list, `*`)

invisible(plot(mri_list2[[1]], doCropping = FALSE))
bhistogram(as.array(mri_list2[[1]]))
```


## Removing the background artifacts from images

```{r}
mri_list <- purrr::map2(mri_list, mask_list, `*`)
scat_list <- purrr::map2(scat_list, mask_list, `*`)
vsat_list <- purrr::map2(vsat_list, mask_list, `*`)
```

```{r}
lobstr::obj_sizes(mri_list, mask_list, scat_list, vsat_list)
```


## Checking generated images

```{r}
testthat::expect_equal(length(mri_list), 80)
testthat::expect_equal(length(mask_list), 80)
testthat::expect_equal(length(scat_list), 80)
testthat::expect_equal(length(vsat_list), 80)
```

```{r}
dims <- purrr::map(mri_list, dim)
testthat::expect_setequal(dims[1], dims)
testthat::expect_setequal(dims[1], purrr::map(mask_list, dim))
testthat::expect_setequal(dims[1], purrr::map(scat_list, dim))
testthat::expect_setequal(dims[1], purrr::map(vsat_list, dim))
```

```{r}
n <- 53
is_na <- purrr::compose(is.na, as.numeric)
testthat::expect_setequal(is_na(mri_list[[n]]), FALSE)
testthat::expect_setequal(is_na(mask_list[[n]]), FALSE)
testthat::expect_setequal(is_na(scat_list[[n]]), FALSE)
testthat::expect_setequal(is_na(vsat_list[[n]]), FALSE)
```

```{r}
in_range <- function(img, rng = 0:255) all(unique(img) %in% rng)

testthat::expect_setequal(
  purrr::map(mri_list, in_range, rng = 0:255), TRUE
)
testthat::expect_setequal(
  purrr::map(mask_list, in_range, rng = 0:1), TRUE
)
testthat::expect_setequal(
  purrr::map(scat_list, in_range, rng = 0:1), TRUE
)
testthat::expect_setequal(
  purrr::map(vsat_list, in_range, rng = 0:1), TRUE
)
```


## [Alpha blending](https://en.wikipedia.org/wiki/Alpha_compositing#Alpha_blending_)

If the mask is opaque, $\alpha = 1$

$$
{\rm blended\ image}_{\rm RGB} = (1 - \alpha)\cdot {\rm image}_{\rm RGB} + \alpha\cdot {\rm mask}_{\rm RGB}
$$
```r
image_RGB <- colorspace::RGB(R = ich1, G = ich2, B = ich3)
mask_RGB <- colorspace::RGB(R = mch1, G = mch2, B = mch3)

blended_RGB <- colorspace::mixcolor(alpha, image_RGB, mask_RGB)
blended_hex <- colorspace::hex(blended_RGB)
```


### An example of blending antsImages

* `alpha == 0` -- transparent mask
* `alpha == 1` -- opaque mask

```{r}
i = 53
alpha = 0.25

mri <- antsImageClone(mri_list[[i]])
mask <- antsImageClone(mask_list[[i]])
scat <- antsImageClone(scat_list[[i]])
vsat <- antsImageClone(vsat_list[[i]])

mri <- mri * mask
scat <- scat * mask
vsat <- vsat * mask
```

```{r eval=FALSE, include=FALSE}
# Neon Rainbow
# https://www.schemecolor.com/neon-rainbow.php
```

```{r figures-blended1, fig.show="hold", fig.asp = 0.5, out.width="33.3%"}
plotBlendedImages(mri, mask, alpha = 0.35, title = i, title_size = 24)
plotBlendedImages(mri, scat, alpha = 0.35, title = i, title_size = 24)
plotBlendedImages(mri, vsat, alpha = 0.35, title = i, title_size = 24)
```


## Image Lists to Tensors

```{r}
mask_alist <- imageList2arrayList(mask_list)
mri_alist <- imageList2arrayList(mri_list)
scat_alist <- imageList2arrayList(scat_list)
vsat_alist <- imageList2arrayList(vsat_list)
```

```{r}
lobstr::obj_sizes(mri_alist, mask_alist, scat_alist, vsat_alist)
```

```{r}
mri_tensor <- arrayList2Tensor(mri_alist)
mask_tensor <- arrayList2Tensor(mask_alist)
scat_tensor <- arrayList2Tensor(scat_alist)
vsat_tensor <- arrayList2Tensor(vsat_alist)
```

```{r}
str(mri_tensor)
lobstr::obj_sizes(mri_tensor, mask_tensor, scat_tensor, vsat_tensor)
```


### Check if dimnames are parallel to image indexes

```{r figures2-side10, fig.show="hold", fig.asp=0.5, out.width="50%"}
plot2_array2d(
  mri_tensor[29,,], mask_tensor[29,,],
  alpha = 0.4,
  title = dimnames(mri_tensor)[[1]][[29]],
  title_size = 24
)
plot2_array2d(
  mri_tensor[29,,],
  alpha = 0.1,
  title = dimnames(mri_tensor)[[1]][[29]],
  title_size = 24
)
```

```{r figures2-side2, fig.show="hold", fig.asp=0.5, out.width="50%"}
plot2_array2d(
  mri_tensor[29,,], scat_tensor[29,,],
  title = dimnames(mri_tensor)[[1]][[29]],
  title_size = 24
)
plot2_array2d(
  mri_tensor[29,,], vsat_tensor[29,,],
  title = dimnames(mri_tensor)[[1]][[29]],
  title_size = 24
)
```

```{r figures2-side3, fig.show="hold", fig.asp=0.5, out.width="50%"}
plot_array2d(scat_tensor[46,,], title = dimnames(scat_tensor)[[1]][[46]])
plot_array2d(scat_tensor["700120",,], title = dimnames(scat_tensor)[[1]][[46]])
```

```{r figures2-side4, fig.show="hold", fig.asp=0.5, out.width="50%"}
plot_array2d(vsat_tensor[51,,], title = dimnames(vsat_tensor)[[1]][[51]])
plot_array2d(vsat_tensor[53,,], title = dimnames(vsat_tensor)[[1]][[53]])
```

```{r}
table(scat_tensor[53,,])
table(vsat_tensor[53,,])
```


## TODO: save tensors in `data-data` raw

```{r}
# use_data_raw(
#   name = "DATASET",
#   open = rlang::is_interactive()
# )
#
# use_data(
#   ...,
#   internal = FALSE,
#   overwrite = FALSE,
#   compress = "bzip2",
#   version = 2
# )
```


## TODO: Resampling Tensors in next file

Use these functions
`ANTsRNet::resampleTensor`, `reticulate::array_reshape`.


## AdvR: missing values

```{r}
NA > 5
NA > NA
10 * NA
!NA
```

```{r}
NA | TRUE
NA & FALSE
```

```{r}
0/0
1/0
-1/0
1/Inf
```

```{r}
# x == NA
empty = c()
is.finite(empty)
empty[is.finite(empty)]
empty[is.na(empty)]
maxi = max(empty[is.finite(empty)])
is.finite(maxi)
cat("---\n")
x <- c(NA, 5, NA, 10)
is.na(x)
is.finite(x)
x[is.finite(x)]
x[!is.na(x)]
max(x[!is.na(x)])
y <- c(NaN, 5, NaN, 10)
is.na(y)
is.finite(y)
y[is.finite(y)]
y[!is.na(y)]
max(y[!is.na(y)])
z <- c(Inf, 5, -Inf, 10)
is.na(z)
is.finite(z)
z[is.finite(z)]
z[!is.na(z)]
max(z[!is.na(z)])
```

```{r}
?max
max(c(1, -Inf))

max(c())
max(NA, na.rm = TRUE)
max(NaN, na.rm = TRUE)

maxi <- max(c())
!is.finite(maxi) | maxi == 0
maxi <- 0
!is.finite(maxi) | maxi == 0
```


## Looking thru colorspace

```{r}
A = c(0.5, 1, 0, NA, NaN, Inf)
B = c(0.5, 1, 0, 0.5, 0.5, 0.5)
tb <- colorspace::RGB(R = A, G = B, B = B)
tb
```

```{r}
col <- colorspace::hex(tb)
col
is.na(col[1])
is.na(col[4])
```

```{r}
ord <- as.character(levels(factor(col)))
ord
ord[2]
```

```{r}
f <- factor(col)
f
levels(f)
```
