---
title: Convert extra MR Images to Tensors
date: 8.12.2020
output:
  html_document:
    keep_html: TRUE
    df_print: paged
  pdf_document: default
---

```{r, include = FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/10_images_to_tensors-",
  out.width = "100%"
)

`%>%` <- purrr::`%>%`

library(tidyverse, warn.conflicts = FALSE)
library(ANTsRCore)

library(devtools)
library(lobstr)
library(fs)

library(rraysplot)
packageVersion("rraysplot")
```


## Helper functions

```{r}
crop_image_wxhx1 <- function(img, ll = c(34, 56), wh = c(768, 384)) {
  ll = c(ll, 1)
  ur = ll + c(wh, 0) - c(1, 1, 0)
  ANTsRCore::cropIndices(img, ll, ur)
}

get_channel <- function(img, channel = 1) {
  ANTsRCore::splitChannels(img)[[channel]]
}

imageList2sliceList <- function(
    iList,
    channel = 1,
    z_slice = 1,
    do_cropping = TRUE,
    lower_left = c(34, 56),
    width_x_height = c(768, 384)
) {
  if (do_cropping == TRUE) {
    iList <- purrr::map(
      iList,
      crop_image_wxhx1, ll = lower_left, wh = width_x_height
    )
  }
  iList <- purrr::map(iList, get_channel, ch = channel)
  iList <- purrr::map(iList,
    ANTsRCore::extractSlice, slice = z_slice, direction = 3
  )
}

imageList2MaskList <- function(iList, clean_up = 2) {
  purrr::map(iList, ANTsRCore::getMask, cleanup = clean_up)
}

imageList2arrayList <- function(iList) {
  purrr::map(iList, as.array)
}

arrayList2Tensor <- function(aList, dim_names = info_mri$patient) {
  tensor <- array(
    data = NA,
    dim = c(length(aList), dim(aList[[1]]))
  )

  for (i in seq_along(aList)) {
    tensor[i,,] <- aList[[i]]
  }
  dimnames(tensor)[[1]] <- dim_names

  tensor
}
```


## Read MR Images Data into Tibble

```{r}
# info <- images_info("../120_images", extension = "dcm")
info <- images_info("../40_images_06.12.2020", extension = "dcm")
```

```{r}
n_patients <- 40
```

```{r, rows.print=2}
info_mri <- info %>% filter(kind == "MRI")
info_mri
```

```{r, rows.print=2}
info_scat <- info %>% filter(kind == "SCAT")
info_scat
```

```{r, rows.print=2}
info_vsat <- info %>% filter(kind == "VSAT")
info_vsat
```


## Create MRI, Mask, SCAT, and VSAT Lists

```{r}
mri_list  <- imageFileNames2ImageList(info_mri[["file_path"]]) %>%
  imageList2sliceList(channel = 1)
mask_list <- imageList2MaskList(mri_list, clean_up = 2)

scat_list <- imageFileNames2ImageList(info_scat[["file_path"]]) %>%
  imageList2sliceList(channel = 1) %>%
  imageList2MaskList(clean_up = 0)

vsat_list <- imageFileNames2ImageList(info_vsat[["file_path"]]) %>%
  imageList2sliceList(channel = 3) %>%
  imageList2MaskList(clean_up = 0)
```

We are going to remove the background noise from image. Why?
see the figure below.

The background noise and artifacts (forearms here) present in image (left)
and removed from image (right).

```{r figures-bgnoise, fig.show="hold", fig.asp=1, out.width="25%"}
invisible(plot(mri_list[[1]], doCropping = FALSE))
bhistogram(as.array(mri_list[[1]]))

img1r <- mri_list[[1]] * mask_list[[1]]

invisible(plot(img1r, doCropping = FALSE))
bhistogram(as.array(img1r))
```


## Background noise and artifacts removal

Removing the background noise and artifacts from MR images.

```{r}
mri_list <- purrr::map2(mri_list, mask_list, `*`)
scat_list <- purrr::map2(scat_list, mask_list, `*`)
vsat_list <- purrr::map2(vsat_list, mask_list, `*`)
```

```{r eval=FALSE, include=FALSE}
lobstr::obj_sizes(mri_list, mask_list, scat_list, vsat_list)
```


## Basic checks on generated images

```{r}
testthat::expect_equal(length(mri_list), n_patients)
testthat::expect_equal(length(mask_list), n_patients)
testthat::expect_equal(length(scat_list), n_patients)
testthat::expect_equal(length(vsat_list), n_patients)
```

```{r}
dims <- purrr::map(mri_list, dim)
testthat::expect_setequal(dims[1], dims)
testthat::expect_setequal(dims[1], purrr::map(mask_list, dim))
testthat::expect_setequal(dims[1], purrr::map(scat_list, dim))
testthat::expect_setequal(dims[1], purrr::map(vsat_list, dim))
```

```{r}
n <- 23
is_na <- purrr::compose(is.na, as.numeric)
testthat::expect_setequal(is_na(mri_list[[n]]), FALSE)
testthat::expect_setequal(is_na(mask_list[[n]]), FALSE)
testthat::expect_setequal(is_na(scat_list[[n]]), FALSE)
testthat::expect_setequal(is_na(vsat_list[[n]]), FALSE)
```

```{r}
in_range <- function(img, rng = 0:255) all(unique(img) %in% rng)

testthat::expect_setequal(
  purrr::map(mri_list, in_range, rng = 0:255), TRUE
)
testthat::expect_setequal(
  purrr::map(mask_list, in_range, rng = 0:1), TRUE
)
testthat::expect_setequal(
  purrr::map(scat_list, in_range, rng = 0:1), TRUE
)
testthat::expect_setequal(
  purrr::map(vsat_list, in_range, rng = 0:1), TRUE
)
```


## [Alpha blending](https://en.wikipedia.org/wiki/Alpha_compositing#Alpha_blending_) masks with images

$$
{\rm blended\ image}_{\rm RGB} = (1 - \alpha)\cdot {\rm image}_{\rm RGB} + \alpha\cdot {\rm background\ mask}_{\rm RGB}
$$

* Set `alpha == 0` -- for transparent background mask.
* Set `alpha == 1` -- for fully opaque mask.

An example of blending antsImages.

```{r}
i = 23
alpha = 0.25

mri <- antsImageClone(mri_list[[i]])
mask <- antsImageClone(mask_list[[i]])
scat <- antsImageClone(scat_list[[i]])
vsat <- antsImageClone(vsat_list[[i]])
```

```{r eval=FALSE, include=FALSE}
# Neon Rainbow
# https://www.schemecolor.com/neon-rainbow.php
```

```{r figures-blended1, fig.show="hold", fig.asp = 0.5, out.width="33.3%"}
plotBlendedImages(mri, mask, alpha = 0.35, title = i, title_size = 24)
plotBlendedImages(mri, scat, alpha = 0.35, title = i, title_size = 24)
plotBlendedImages(mri, vsat, alpha = 0.35, title = i, title_size = 24)
```


## Image Lists to Tensors

```{r}
mask_alist <- imageList2arrayList(mask_list)
mri_alist <- imageList2arrayList(mri_list)
scat_alist <- imageList2arrayList(scat_list)
vsat_alist <- imageList2arrayList(vsat_list)
```

```{r eval=FALSE, include=FALSE}
lobstr::obj_sizes(mri_alist, mask_alist, scat_alist, vsat_alist)
```

```{r}
mri_tensor <- arrayList2Tensor(mri_alist)
mask_tensor <- arrayList2Tensor(mask_alist)
scat_tensor <- arrayList2Tensor(scat_alist)
vsat_tensor <- arrayList2Tensor(vsat_alist)
```

```{r eval=FALSE, include=FALSE}
str(mri_tensor)
lobstr::obj_sizes(mri_tensor, mask_tensor, scat_tensor, vsat_tensor)
```

```{r figures3-side10, fig.show="hold", fig.asp=0.5, out.width="33%"}
plot2_array2d(
  mri_tensor[29,,], mask_tensor[29,,],
  title = dimnames(mri_tensor)[[1]][[29]],
  title_size = 24
)
plot2_array2d(
  mri_tensor[29,,], scat_tensor[29,,],
  title = dimnames(mri_tensor)[[1]][[29]],
  title_size = 24
)
plot2_array2d(
  mri_tensor[29,,], vsat_tensor[29,,],
  title = dimnames(mri_tensor)[[1]][[29]],
  title_size = 24
)
```

```{r}
table(mask_tensor[29,,])
table(scat_tensor[29,,])
table(vsat_tensor[29,,])
```


## Save tensors in `data-raw` directory

```{r}
str(mri_tensor)
str(mask_tensor)
str(scat_tensor)
str(vsat_tensor)
```

```{r}
fat40e1_768x384 = list(
  image = mri_tensor,
  mask = mask_tensor,
  scat = scat_tensor,
  vsat = vsat_tensor
)
```

```{r eval=FALSE, include=FALSE}
# usethis::use_data_raw(name = "fat120_768x384")
# usethis::use_data(fat120_768x384, overwrite = TRUE)
usethis::use_data(fat40e1_768x384, overwrite = TRUE)
cat("Move the fat40e1_768x384 from data/ to data-raw/ directory.\n")
fs::file_move(
  "data/fat40e1_768x384.rda", "data-raw/fat40e1_768x384.rda"
)
```
