---
title: Contact Sheets 
date: 22.11.2020
output:
  html_document:
    keep_html: TRUE
    df_print: paged
  pdf_document: default
---

```{r setup, include = FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "data-contact-sheets/fat80_768x384-",
  out.width = "100%"
)

`%>%` <- purrr::`%>%`
`%<-%` <- zeallot::`%<-%`
  
options(buildtools.check = NULL)
# devtools::install_github('r-lib/ragg')
# install.packages("zeallot")
# install.packages("patchwork")
```

```{r}
inch <- function(w, h, ppi) sqrt((w/ppi)^2 + (h/ppi)^2)
inch(5120, 2880, ppi = 218) # iMac
inch(2560, 1600, ppi = 227) # MacBook Pro
```

[Using a Retina display](https://support.apple.com/en-us/HT202471),
[dpilove](https://dpi.lv/#27″):

1. 27-inch iMac models introduced in 2014 or later. 
   Native resolution: 5120 x 2880 (16:9) at 218 ppi (pixels per inch).
   Models introduced in 2014 and 2015 support millions of colors,
   and models introduced in 2017 or later support one billion colors.
   Approx. 23 x 13 in.
1. 13-inch MacBook Pro models introduced in late 2012 or later. 
   Native resolution: 2560 x 1600 (16:10) at 227 ppi.
   Support for millions of colors.
   Approx 11 x 7 in.
   

[Taking Control of Plot Scaling](https://www.tidyverse.org/blog/2020/08/taking-control-of-plot-scaling/).

```{r}
library(tidyverse, warn.conflicts = FALSE)
library(patchwork)
library(ragg)
library(zeallot)

library(rraysplot)
packageVersion("rraysplot", lib.loc = "~/Library/R/4.0/library/")
```

*iMac*, *MacBook Pro* width and height in cm

```{r}
c(3240, 1080) / 218        # in
c(3240, 1080) / 218 * 2.54 # cm
c(2160, 720) / 227         # in
c(2160, 720) / 227 * 2.54  # cm
```

```{r}
# agg_jpeg(width = 3240, height = 1080, res = 218, 
#   scaling = 1, quality = 100)
# agg_jpeg(
#   width = 2160, height = 720, res = 227,
#   scaling = 1, quality = 100
# )
```

```{r}
c(
  c(image_train, ., scat_train, vsat_train),
  c(image_test, ., scat_test, vsat_test)
) %<-% rraysplot::fat80_768x384
```

```{r}
dim(image_test)
```

```{r}
(patients <- dimnames(image_test)[[1]])
```


## Patchworks

```{r}
i = 3
patient <- patients[i]
img = image_test[patient,,]
scat = scat_test[patient,,]
vsat <- vsat_test[patient,,]

contact_sheet <- function(patient, image, scat, vsat) {
  p1 <- rraysplot::plot_array2d(
    image, 
    title = patient, title_size = 10)
  p2 <- rraysplot::plot2_array2d(
    image, scat,
    title = "SCAT", title_size = 9, alpha = 0.8)
  p3 <- rraysplot::plot2_array2d(
    image, vsat, 
    title = "VSAT", title_size = 9, alpha = 0.6)
  
  print(p1 | p2 | p3)
}
```

```{r contact-sheet, fig.show="hold", fig.asp = 0.24, out.width="100%"}
contact_sheet(patient, img, scat, vsat)
```

```{r}
contact_sheets <- function(
  data = rraysplot::fat80_768x384,
  kind = "test",
  directory = "data-contact-sheets",
  prefix = "768x384"
) {
  patients = dimnames(data[[kind]]$image)[[1]]

  for (patient in patients) {
    img = data[[kind]]$image[patient,,]
    scat = data[[kind]]$scat[patient,,]
    vsat <- data[[kind]]$vsat[patient,,]
    
    if (!fs::dir_exists(directory)) fs::dir_create(directory)

    jpegfile <- fs::path(
      directory, stringr::str_c(kind, "-768x384-", patient, ".jpeg")
    )
    agg_jpeg(jpegfile,
      width = 2160, height = 518, units = "px", res = 227,
      # width = 3240, height = 777, units = "px", res = 218,
      scaling = 1
    )
    contact_sheet(patient, img, scat, vsat)
    invisible(dev.off())
  }
}
```

```{r}
contact_sheets(
  data = rraysplot::fat80_768x384,
  kind = "test",
  directory = "data-contact-sheets",
  prefix = "768x384"
)
```

```{r}
contact_sheets(
  data = rraysplot::fat80_768x384,
  kind = "train",
  directory = "data-contact-sheets",
  prefix = "768x384"
)
```
