---
title: Contact Sheets 
date: 25.11.2020
output:
  html_document:
    keep_html: TRUE
    df_print: paged
  pdf_document: default
---

1. [28 Graphics for communication](https://r4ds.had.co.nz/graphics-for-communication.html):
    * [28.7.1 Figure sizing](https://r4ds.had.co.nz/graphics-for-communication.html#figure-sizing)

If you want to make sure the font size is consistent across 
all your figures, whenever you set out.width,
you’ll also need to adjust fig.width to maintain
the same ratio with your default out.width. 

For example, if your default `fig.width` is 6 and 
`out.width` is 0.7, when you set `out.width = "50%"` 
you’ll need to set `fig.width` to 4.3 (6 * 0.5 / 0.7).

```{r}
adjust_fig_width <- function(
    fig_width = 6, old_out_width = 70, new_out_width = 50) {
  round(fig_width * new_out_width / old_out_width, digits = 1)
}
# adjust_fig_width()                    # 4.3
# adjust_fig_width(old_out_width = 100) # 3
```


```{r setup, include = FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  fig.retina = TRUE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "data-contact-sheets/fat80_768x384-",
  fig.width = 6,
  fig.asp = 0.618,
  out.width = "100%"
)

`%>%` <- purrr::`%>%`
`%<-%` <- zeallot::`%<-%`
  
options(buildtools.check = NULL)
# devtools::install_github('r-lib/ragg')
# install.packages("zeallot")
# install.packages("patchwork")
```

```{r}
inch <- function(w, h, ppi) sqrt((w/ppi)^2 + (h/ppi)^2)
inch(5120, 2880, ppi = 218) # iMac 27"
inch(2560, 1600, ppi = 227) # MacBook Pro 13.3"
```

[Using a Retina display](https://support.apple.com/en-us/HT202471),
[dpilove](https://dpi.lv/#27″):

1. 27-inch iMac models introduced in 2014 or later. 
   Native resolution: 5120 x 2880 (16:9) at 218 ppi (pixels per inch).
   Models introduced in 2014 and 2015 support millions of colors,
   and models introduced in 2017 or later support one billion colors.
   Approx. 23 x 13 in.
1. 13-inch MacBook Pro models introduced in late 2012 or later. 
   Native resolution: 2560 x 1600 (16:10) at 227 ppi.
   Support for millions of colors.
   Approx 11 x 7 in.
   

[Taking Control of Plot Scaling](https://www.tidyverse.org/blog/2020/08/taking-control-of-plot-scaling/).

```{r}
library(tidyverse, warn.conflicts = FALSE)
library(patchwork)
library(ragg)
library(zeallot)

library(rraysplot)
packageVersion("rraysplot", lib.loc = "~/Library/R/4.0/library/")
```

*iMac*, *MacBook Pro* width and height in cm

```{r}
c(3240, 1080) / 218        # in
c(3240, 1080) / 218 * 2.54 # cm
c(2160, 720) / 227         # in
c(2160, 720) / 227 * 2.54  # cm
```
## Helper functions

```{r}
contact_sheet <- function(patient, image, scat, vsat) {
  p1 <- rraysplot::plot_array2d(
    image, 
    title = patient, title_size = 10)
  p2 <- rraysplot::plot2_array2d(
    image, scat,
    title = "SCAT", title_size = 9, alpha = 0.8)
  p3 <- rraysplot::plot2_array2d(
    image, vsat, 
    title = "VSAT", title_size = 9, alpha = 0.6)
  
  print(p1 | p2 | p3)
}
```

```{r}
contact_sheets <- function(
  data = rraysplot::fat80_768x384,
  kind = "test",
  directory = "data-contact-sheets",
  prefix = "768x384"
) {
  patients = dimnames(data[[kind]]$image)[[1]]

  for (patient in patients) {
    img = data[[kind]]$image[patient,,]
    scat = data[[kind]]$scat[patient,,]
    vsat <- data[[kind]]$vsat[patient,,]
    
    if (!fs::dir_exists(directory)) fs::dir_create(directory)

    jpegfile <- fs::path(
      directory, stringr::str_c(kind, "-768x384-", patient, ".jpeg")
    )
    agg_jpeg(jpegfile,
      width = 2160, height = 518, units = "px", res = 227,
      # width = 3240, height = 777, units = "px", res = 218,
      scaling = 1
    )
    contact_sheet(patient, img, scat, vsat)
    invisible(dev.off())
  }
}
```


## Read Test and Train Tensors

```{r}
c(
  c(image_train, ., scat_train, vsat_train),
  c(image_test, ., scat_test, vsat_test)
) %<-% rraysplot::fat80_768x384
```

```{r}
dim(image_test)
dim(image_test)
```

```{r}
dimnames(image_test)[[1]]
cat("\n")
dimnames(image_train)[[1]]
```

## Display Broken Images

Broken masks for test images.

```{r}
patient_contact_sheet <- function(patient, set = "test") {
  img  = eval(sym(stringr::str_c("image_", set)))[patient,,]
  scat  = eval(sym(stringr::str_c("scat_", set)))[patient,,]
  vsat  = eval(sym(stringr::str_c("vsat_", set)))[patient,,]
  
  contact_sheet(patient, img, scat, vsat)
}
```

```{r}
broken_test_masks <- c("1110505-2012")
```

```{r test-mask-1, echo=FALSE, fig.asp=0.24, fig.show="hold", out.width="100%"}
patient_contact_sheet(broken_test_masks[1], set = "test")
```


```{r}
broken_train_masks <- c("600725-2013", "806365", "858488")
```

```{r contact-sheet, echo=FALSE, fig.asp=0.24, fig.show="hold", out.width="100%"}
patient_contact_sheet(broken_train_masks[1], set = "train")
patient_contact_sheet(broken_train_masks[2], set = "train")
patient_contact_sheet(broken_train_masks[3], set = "train")
```



## Save only images with correctly computed masks

```{r eval=FALSE, include=FALSE}
contact_sheets(
  data = rraysplot::fat80_768x384,
  kind = "test",
  directory = "data-contact-sheets",
  prefix = "768x384"
)
```

```{r eval=FALSE, include=FALSE}
contact_sheets(
  data = rraysplot::fat80_768x384,
  kind = "train",
  directory = "data-contact-sheets",
  prefix = "768x384"
)
```
