---
output: github_document
---

See [3.1 HTML document](https://bookdown.org/yihui/rmarkdown/html-document.html)
in „R Markdown: The Definitive Guide” by Yihui Xie, J. J. Allaire, Garrett Grolemund.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "figures/devworkflow-",
  out.width = "100%"
)

`%>%` <- purrr::`%>%`
```

```{r}
library(devtools)
library(fs)
```

```{r}
fs::dir_info(
    all = TRUE,
    recurse = TRUE,
    regexp = "^(.git|.Rproj.user|.+\\.(html|md))/.+",
    invert = TRUE) %>% 
  dplyr::select(path, type)
```

## [2.6 Write the first function](https://r-pkgs.org/whole-game.html#write-the-first-function)

```r
use_r("make_arrays")
```

Put the following definition in _R/make_arrays.R_ an save it.

```r
make_arrays <- function(m = 5, n = 5) {
  array(NA, c(m, n))
}
```

```r
load_all() # shift + ctrl + L  or  shift + command

make_arrays(2, 4)
#>      [,1] [,2] [,3] [,4]
#> [1,]   NA   NA   NA   NA
#> [2,]   NA   NA   NA   NA
```

```r
check()
```


## 2.10 Edit DESCRIPTION

```{r}
use_mit_license("Wlodek Bzyl")
# ✓ Setting active project to '/Users/wbzyl/RPKGS/GUMED/rraysplot'
# ✓ Writing 'LICENSE.md'
# ✓ Adding '^LICENSE\\.md$' to '.Rbuildignore'
# ✓ Writing 'LICENSE'
```

```r
check()
```


## 2.12 document()

Would not it be nice to get help on `make_arrays()`, just like we do with other R functions?
This requires that your package have a special R documentation file, _man/make_arrays.Rd_.

```r
document()
# Updating rraysplot documentation
# Loading rraysplot
# Writing NAMESPACE
# Writing make_arrays.Rd
```

```r
check()
```


## 2.14 `install()`

Since we have a minimum viable(?) product now, let’s install the foofactors
package into your library via `install()`:

```{r}
install()
# * installing to library ‘/Users/wbzyl/Library/R/4.0/library’
```

```{r}
library(rraysplot)
make_arrays(2, 3)
```


## 2.15 `use_testthat()`

* [testthat](https://testthat.r-lib.org) -- overview, reference, articles.

```{r}
use_testthat()
# ✓ Adding 'testthat' to Suggests field in DESCRIPTION
# ✓ Creating 'tests/testthat/'
# ✓ Writing 'tests/testthat.R'
# ● Call `use_test()` to initialize a basic test file and open it for editing.
```

```{r}
use_test("make_arrays")
# ✓ Writing 'tests/testthat/test-make_arrays.R'
# ● Modify 'tests/testthat/test-make_arrays.R'
```

```{r}
library(testthat)
load_all()
```

```{r}
test() # cmd + shift + T
```

