---
title: "Creating R package -- first steps"
output:
  html_document:
    df_print: paged
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  # fig.path = "figures/README-",
  out.width = "100%"
)

`%>%` <- purrr::`%>%`
```

## More info...

* Package structure and state. 
[4.7 Package libraries](https://r-pkgs.org/package-structure-state.html#library).
* [Comparison of `fs` functions, base R, and shell commands](https://cran.r-project.org/web/packages/fs/vignettes/function-comparisons.html)


## Managing package libraries

Here are the main two levers that control which libraries
are active, in order of scope and persistence:

1. Environment variables, like `R_LIBS` and `R_LIBS_USER`,
which are consulted at startup.
1. Calling `.libPaths()` with one or more filepaths.

```sh
mkdir -p ~/Library/R/4.0/library
```

```{sh}
cat ~/.Rprofile.site
```

```{sh}
echo $R_LIBS_USER
```

```{r}
.Library
.Library.site
```

In both cases we see two active libraries, consulted in this order:

1. A user library.
1. A system-level or global library.

```{r}
.libPaths()
```

```{r}
lapply(
  .libPaths(), 
  list.dirs, 
  recursive = FALSE, 
  full.names = FALSE)
```


## Check what is installed

```{r message=FALSE, warning=FALSE}
packageVersion("devtools")

options(buildtools.check = NULL)
# devtools::install_github("r-lib/devtools")
# packageVersion("devtools")
```

Optionally run:

```{r}
# tidyverse::tidyverse_update()
# tidyverse::tidyverse_conflicts()
tidyverse::tidyverse_packages()
```


## [Name your package](https://r-pkgs.org/workflows101.html#naming)

There are three formal requirements:

1. The name can only consist of letters,
   numbers, and periods.
1. It must start with a letter.
1. It cannot end with a period.

Unfortunately, this means you can’t use either
hyphens (`-`) or underscores (`_`) in your package name.
We recommend against using periods in package names,
due to confusing associations with file 
extensions and S3 methods.

The [available](https://cran.r-project.org/web/packages/available/available.pdf) 
package has a function called `available()` that helps
you evaluate a potential package name from many angles:

```r
devtools::install_github("ropenscilabs/available")
```

```{r}
available::suggest(text = "Plotting helpers for arrays.")
```


## [Create package](https://r-pkgs.org/workflows101.html#create-a-package)

```{r}
library(devtools)
library(tidyverse)
```

```{r}
source_directory <- "~/RPKGS/GUMED" 
package_name <- "rraysplot"

# fs::dir_create(source_directory)

pkg_path <- fs::path(.libPaths()[[1]], package_name)
pkg_path
src_path <- fs::path(source_directory, package_name)
src_path
```

```r
usethis::create_package(src_path)
```

```
✓ Creating '/Users/wbzyl/RPKGS/GUMED/rraysplot/'
✓ Setting active project to '/Users/wbzyl/RPKGS/GUMED/rraysplot'
✓ Creating 'R/'
✓ Writing 'DESCRIPTION'
Package: rraysplot
Title: What the Package Does (One Line, Title Case)
Version: 0.0.0.9000
Authors@R (parsed):
    * Wlodek <wlodek@rpkgs.com> [aut, cre]
Description: What the package does (one paragraph).
License: MIT + file LICENSE
Encoding: UTF-8
LazyData: true
Roxygen: list(markdown = TRUE)
RoxygenNote: 7.1.1
✓ Writing 'NAMESPACE'
✓ Writing 'rraysplot.Rproj'
✓ Adding '.Rproj.user' to '.gitignore'
✓ Adding '^rraysplot\\.Rproj$', '^\\.Rproj\\.user$' to '.Rbuildignore'
✓ Opening '/Users/wbzyl/RPKGS/GUMED/rraysplot/' in new RStudio session
✓ Setting active project to '<no active project>'
```

```{r}
fs::dir_info(
    all = TRUE,
    recurse = TRUE,
    regexp = "^(.git|.Rproj.user)/.+",
    invert = TRUE) %>% 
  dplyr::select(path, type)
```
